\chapter{Multipath TCP}
\label{chap:multipathtcp}

From now on the discussion becomes more technical. This chapter is all about how MPTCP works from a technical perspective. In this chapter there is no reference about the work carried out during the stage but only information taken from external documentation.

\section{Transmission Control Protocol (TCP)}
This is an explanation on how plain TCP protocol works. Even if there is no need to go into too much details here, this is a necessary starting point from where the MPTCP extension discussion can start (in the next section).

\section{MPTCP Design}
How MPTCP is added on top of TCP (with all the related design aspects) is reported here. This is the first portion of the thesis containing a more in-depth description of how MPTCP works in the networking stack. This specific section might follow closely the introductory portions of the RFC documents regarding MPTCP.

\subsection{Control Plane}
All the MPTCP options used to manage MPTCP sessions are reported and explained here, including all the details on how to set a new session and add/remove subflows.

\subsection{Data Plane}
This part concerns all the MPTCP options used to manage the data flow in a MPTCP session, including how the byte stream is subdivided into different subflow and how the original order of the packets is provided at the receiver.

\section{MPTCP Deployment}
After having explained all the technicalities about the protocol, it is now possible to talk about its deployment status and the problems encountered by pairing MPTCP with current infrastructures. This might seem a bit outside the scope of the thesis, but it is worth mentioning that the \textit{deployment status} and \textit{implementations} are a good indicator of how much MPTCP is important in the Internet community and they are good topics to motivate the thesis work. Also \textit{middleboxes compatibility} is indeed a fundamental part of the MPTCP security evaluation, being monitoring and detection equipment part of these middleboxes.

\subsection{Middleboxes Compatibility}
This section will be quite technical and it is supposed to list the most important middle-boxes and their impact/effect on a MPTCP connection. These boxes include NATs, proxies and firewalls. This part should clearly state why MPTCP widespread adoption is a big challenge.

\subsection{Implementations}
Despite the previously described problematics, MPTCP is a big bet in the IETF community and many implementations have been developed for the most common OSes, listed in this section (with some history notions).

\subsection{Deployment Status}
It should be interesting for the reader to go through some examples of real world's scenarios in which MPTCP is used successfully. Here it is possible to cite some important achievements related to MPTCP (for example the highest throughput ever reached with the new protocol).
If available, it would be also good to show some graphs about MPTCP adoption rate or similar.