\documentclass[pdfa,11pt,english]{toptesi}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\usepackage[utf8]{inputenc} %utf8
\usepackage[english]{babel}
\usepackage[T1]{fontenc}
\usepackage{blindtext}
\usepackage{graphicx,wrapfig}
\usepackage{booktabs}
\usepackage{lmodern}
\usepackage{varioref}
\usepackage{url}
\usepackage{array}
\usepackage{paralist}{\obeyspaces\global\let =\space}
\usepackage{verbatim} 
\usepackage{subfig}
\usepackage{tabularx}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{float}
\usepackage{amssymb}
\usepackage{multicol}
\usepackage{multirow}
\usepackage{listings}
\usepackage[pass]{geometry}
\usepackage[figuresright]{rotating}
\usepackage{algorithm}
\usepackage{algorithmic}
\usepackage{amsmath}
\usepackage[babel]{csquotes}
\usepackage{hyperref}
\usepackage[backend=bibtex,sorting=none]{biblatex}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% CONFIGURAZIONE LINK E RIFERIMENTI
\hypersetup{%
    pdfpagemode={UseOutlines},
    bookmarksopen,
    pdfstartview={FitH},
    colorlinks,
    linkcolor={black}, %COLORE DEI RIFERIMENTI AL TESTO
    citecolor={blue}, %COLORE DEI RIFERIMENTI ALLE CITAZIONI
    urlcolor={blue} %COLORI DEGLI URL
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% CONFIGURAZIONE LISTATI/CODICE - CANCELLARE SE NON NECESSARIO
% PYTHON - BIANCO E NERO
\lstset{%
	captionpos=b,
	language=Python,
	basicstyle =\small\ttfamily,
	keywordstyle=\color{black}\bfseries,
	breaklines=true,
	breakatwhitespace=true,
	frame=lines,
	showstringspaces=false,
	numbers=left,
	numberstyle=\footnotesize,
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%DEFINIZIONE SEZIONI IN NUMERAZIONE ROMANA
%ELENCO DEI LISTATI/CODICI
\makeatletter
\newcommand\listofcodes{%
 \iffrontmatter\else\frontmattertrue\fi
 \if@openright\cleardoublepage\else\clearpage\fi
 % change the meaning of \chapter in a group
 \begingroup\def\chapter##1{\@schapter}
 \phantomsection % for the hyperlink
 \lstlistoflistings 
 \endgroup
} 
\makeatother

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% INFORMAZIONI PDF - PERSONALIZZARE
\pdfinfo{%
  /Title    (Security Evaluation of Multipath TCP)
  /Author   (Fabrizio Demaria)
  /Subject  (Analyzing and fixing Multipath TCP vulnerabilities, contributing to the Linux Kernel implementation of the new version of the protocol)
  /Keywords (MPTCP Security)
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% FRONTESPIZIO - PERSONALIZZARE
% ELIMINATE LE VOCI CHE NON VI SERVONO

% UNIVERSITA - NOME
\ateneo{Polytechnic of Turin - Stockholm's KTH}

% FACOLTA - DICITURA
\FacoltaDi{Faculty of }
% FACOLTA - NOME
\facolta{Engineering}

% CORSO DI LAUREA - DICITURA (MANTENERE LO SPAZIO)
\CorsoDiLaureaIn{Master of Science in }
% CORSO DI LAUREA - NOME
\corsodilaurea{Computer Engineering}

% TIPOLOGIA TESI
\TesiDiLaurea{Master Thesis}

% TITOLO
\titolo{Security Evaluation of Multipath TCP}

% SOTTOTITOLO
\sottotitolo{Analyzing and fixing Multipath TCP vulnerabilities, contributing to the Linux Kernel implementation of the new version of the protocol}

% RELATORE/I - DICITURA
\AdvisorName{Advisors}
% RELATORE - PROF. NOME E COGNOME
\relatore{prof.\ Antonio Lioy}
% RELATORE AGGIUNTIVO - PROF NOME E COGNOME
% SE SI HA SOLO UN RELATORE ELIMINARE E CAMBIARE Advisors in Advisor
\secondorelatore{prof.\ Peter Sjödin}

% TUTORE AZIENDALE - TITOLO NOME E COGNOME
\tutoreaziendale{Henrik Svensson\\Joakim Nordell\\Shujuan Chen}
% TUTORE AZIENDALE - DICITURA//AZIENDA
\NomeTutoreAziendale{Company tutors\\Intel Corporation}

% CANDIDATO - DICITURA (MANTENERE I DUE PUNTI)
\CandidateName{Candidate:}
% SECONDO CANDIDATO - ELIMINARE O DECOMMENTARE
%secondocandidato{Bombo de Bombis}

% CANDIDATO - NOME E COGNOME
\candidato{Fabrizio Demaria}

% LOGO UNIVERSITA
\logosede{images/logo}

% DATA - MESE ANNO
\sedutadilaurea{March 2016}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% LISTA DEI CAPITOLI DA INCLUDERE - PERSONALIZZARE
\includeonly{%
  chap_introduction,%
  chap_multipathtcp,%
  chap_mptcpsecurity,%
  chap_addaddrattackexecution,%
  chap_addaddr2,%
  chap_conclusions,%
  app_a,%
  app_b,%
}

% FILE DI BIBLIOGRAFIA
\bibliography{bibliography} 

% FILE COMANDI DA TEMPLATE LIOY
\input{commands.tex}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% INIZIO DOCUMENTO
\begin{document}
\english

\frontespizio
\paginavuota

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%INTERLINEA - DEFAULT 1
\interlinea{1.1}
%\advance\voffset -5mm
%\advance\textheight 30mm

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\frontmatter

% DEDICA - PERSONALIZZARE
% VSPACE - PROPORZIONE USATA PER CENTRATURA VERTICALE DEL TESTO
% FLUSHRIGHT - ALLINEAMENTO ORIZZONTALE A DESTRA
%\vspace*{\stretch{1}}
%\begin{flushright}
%\noindent
%To...
%\end{flushright}
%\vspace*{\stretch{6}}
%\cleardoublepage

% CITAZIONE - PERSONALIZZARE
% VSPACE - PROPORZIONE USATA PER CENTRATURA VERTICALE DEL TESTO
% FLUSHRIGHT - ALLINEAMENTO ORIZZONTALE A DESTRA
%\vspace*{\stretch{1}}
%\begin{flushright}
%\noindent
%Citation

%\textit{cit.}%
%\end{flushright}
%\vspace*{\stretch{6}}
%\cleardoublepage

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% RINGRAZIAMENTI - PERSONALIZZARE
\ringraziamenti
This Thesis work has been carried out at the Intel Corporation office of Lund (Sweden), during a period of six months from September 2015 to February 2016. Before starting this project I spent one year in Stockholm, studying at KTH University as an Erasmus student originally from Turin, Italy.

The first persons I would like to thank are my family and friends from Italy, who supported me from far away during my studies in Sweden and during the whole time dedicated to this Thesis. I also would like to thank the people that supported me from a closer distance, in particular the Swedish family I have lived with during the six months of the Thesis project, that was very friendly to me.
I would like to thank all the people from the office, who integrated me very well despite my poor skills in speaking Swedish. 
I would like to thank my manager Henrik Svensson for giving me the possibility of working on such an valuable and interesting project. Special thanks go to the two Intel engineers that closely followed my work at the Lund office: Joakim Nordell and Shujuan Chen. 
The work involved other major stakeholders, passionate about the Multipath TCP project, who supported me in the development phase: in these regards, I'd like to thank Doru Gucea, Vlad Dogaru and Octavian Purdila. 
A special thank you goes to Christoph Paasch from Apple California, who directed the whole development process from the other side of the world, helping me in the process and finally accepting my contribution to the official Multipath TCP source code for the Linux Kernel.
This work has been supported by both the Polytechnic of Turin and Stockholm's KTH University and I want to thank all the professors I encountered during my academic career, especially the ones that followed this very project from the start until the final discussion: Antonio Lioy from Turin and Peter Sjödin from Stockholm.

It is impossible to mention all the enriching people that I met during my months abroad and all the inspiring experiences lived in this last phase of my academic career, but they all define the fundamental context that made this Thesis work possible. 

Thank you.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% ABSTRACT - PERSONALIZZARE
\sommario
I consider this project on Multipath TCP very interesting because it will potentially affect the whole global networking scenario in a future not too far from now. Multipath TCP aims at achieving the ``next level'' when it comes to standard network communication and it is exciting to be part of this process. 
During the Thesis work, patches have been developed for the Linux Kernel implementation of Multipath TCP: such patches mark the first step towards the new version of the protocol, MPTCP version 1. During the work, contributions have been also produced for the official RFC documentation for Multipath TCP, as well as contributions for related open-source projects, like the famous packet analyzer Wireshark.
Indeed, the part that I loved the most about this work is that it gave me the possibility of positively interacting with important open-source communities, especially the Linux Kernel one. This is a big personal achievement as well as an important step for my working career that just started.
Multipath TCP is an ongoing project subjected to constant changes regarding the protocol and its implementation: this work is just a single step in the overall deployment process and I hope this will not remain my only contribution for Multipath TCP in the future.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% INDICI - ELIMINARE GLI INDICI NON NECESSARI

% INDICE GENERALE
\tableofcontents

% INDICE DELLE FIGURE
%\listoffigures

% INDICE DELLE TABELLE
%\listoftables

% INDICE DEI CODICI
%\listofcodes

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\paginavuota
\mainmatter

% INCLUSIONE FILE CAPITOLI - PERSONALIZZARE - TENERE COERENTE CON LISTA IN ALTO
\include{chap_introduction}
\include{chap_multipathtcp}
\include{chap_mptcpsecurity}
\include{chap_addaddrattackexecution}
\include{chap_addaddr2}
\include{chap_conclusions}

\appendix
% INCLUSIONE APPENDICI - - PERSONALIZZARE - TENERE COERENTE CON LISTA IN ALTO
\include{app_a}
\include{app_b}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% BIBLIOGRAFIA
\addcontentsline{toc}{chapter}{\refname}
\nocite{*}
\printbibliography

\end{document}